### 2015-07-08 narrative/data-reduction.tex
editing 1.3.2

The classical workflow whereby the entire dataset is written to storage for
later analysis is no longer viable owing to the sheer amount of data being
generated. In future, it will be vital to take advantage of a priori
information when 1) writing and reading from the SSIO layer in order to gain
performance and predictability, and to prioritize I/O so that the data that
is most useful for end-user can be written in the time available, and 2) in
performing {\em in situ} operations and analysis before storing the information.

@@

There are many possibilities for refactoring and the best choice will generally
vary from case to case but, once settled, will not change from run to run. It
will be important to understand when the time and resources required to
identify and perform the ``best methods'' outweighs any eventual gains. Another
critical research question concerns the quantification and control of the loss
of information resulting from refactoring the data and using a reduced dataset.

>>>>

The classical workflow where the entire dataset is written to storage for
later analysis is no longer viable simply because the amount of generated data is too large.
In future, it will be vital to take advantage of a priori
information when 1) writing and reading from the SSIO layer in order to gain
performance and predictability, and to prioritize I/O so that the data that
is most useful for end-user can be written in the time available, and 2)
performing {\em in situ} operations and analysis before storing the information.

@@

There are many possibilities for refactoring and the best choice will generally
vary from case to case but, once settled, will typically not change from run to run. It
will be important to understand when the time and resources required to
identify and perform the ``best methods'' outweighs any eventual gains. Another
critical research question concerns the quantification and control of the loss
of information resulting from refactoring the data and using a reduced dataset.
